---
title: "Bible API Analysis"
output: html_notebook
fig_width: 10 
fig_height: 10 
---

# Analysing one bible

### Setup Rest
```{r}
# install.packages("httr")
require("httr")
```

```{r}
# install.packages("jsonlite")
require("jsonlite")
```

We need these two packages in order to interface with [our FastAPI](https://github.com/jimbob88/bible_api/tree/master/api).

### Load URL
```{r}
base_url = "http://127.0.0.1:8000/text_query"
new_url = paste(base_url, '?bible_name=engwebpb_vpl&book=GEN', sep="")
get_data = content(GET(new_url), "text", encoding="utf8")
data_json = fromJSON(get_data, flatten = TRUE)
```

Load the JSON Rest response for the whole of Genesis in [The World English Bible](https://ebible.org/details.php?id=engwebpb).

### Convert to dataframe
```{r}
dataset_raw = do.call(rbind.data.frame, data_json["r"])
```

Convert the response list to a dataframe with headers.

### Load tidytext
```{r}
# install.packages("tidytext")
# install.packages("tidyverse")
library(tidytext)
library(dplyr)
```


### Convert to tibble
```{r}
dataset_web <- as_tibble(dataset_raw)
per_word <- dataset_web %>%
  unnest_tokens(word, verseText)
```

Convert it to a table of tokens (each individual word is ar ow in the tibble)

```{r}
data(stop_words)
per_word <- per_word %>%
  anti_join(stop_words)
per_word %>%
  count(word, sort = TRUE) 
```
Count the freuqency of words

### Plotting
```{r}
# install.packages("ggplot2")
library(ggplot2)
```

```{r}
per_word %>%
  count(word, sort = TRUE) %>%
  filter(n > 100) %>%
  mutate(word = reorder(word, n)) %>%
  ggplot(aes(n, word)) +
  geom_col() +
  labs(y = NULL)
```
Plot the most common word frequencies

# Comparing Multiple Bibles
```{r}
library(tidyr)
library(stringr)
```

### Reload [The World English Bible](https://ebible.org/details.php?id=engwebpb)
```{r}
web_url = paste(base_url, '?bible_name=engwebpb_vpl&book=GEN', sep="")
get_data = content(GET(web_url), "text", encoding="utf8")
data_json = fromJSON(get_data, flatten = TRUE)
dataset_raw = do.call(rbind.data.frame, data_json["r"])
dataset_web <- as_tibble(dataset_raw)
dataset_web <- dataset_web  %>%
  unnest_tokens(word, verseText) %>%
  anti_join(stop_words)
```
### Reload [The American Standard Version](https://ebible.org/details.php?id=eng-asv)
```{r}
asv_url = paste(base_url, '?bible_name=eng_asv_vpl&book=GEN', sep="")
get_data = content(GET(asv_url), "text", encoding="utf8")
data_json = fromJSON(get_data, flatten = TRUE)
dataset_raw = do.call(rbind.data.frame, data_json["r"])
dataset_asv <- as_tibble(dataset_raw)
dataset_asv <- dataset_asv  %>%
  unnest_tokens(word, verseText) %>%
  anti_join(stop_words)
```
### Load [The King James Version](https://ebible.org/details.php?id=eng-kjv2006)
```{r}
kjv_url = paste(base_url, '?bible_name=eng_kjv2006_vpl&book=GEN', sep="")
get_data = content(GET(kjv_url), "text", encoding="utf8")
data_json = fromJSON(get_data, flatten = TRUE)
dataset_raw = do.call(rbind.data.frame, data_json["r"])
dataset_kjv <- as_tibble(dataset_raw)
dataset_kjv <- dataset_kjv  %>%
  unnest_tokens(word, verseText) %>%
  anti_join(stop_words)
```
### Compare the frequency of words against The King James Version

```{r}
frequency <- bind_rows(mutate(dataset_kjv, bible = "King James Version"),
                       mutate(dataset_asv, bible = "American Standard Version"), 
                       mutate(dataset_web, bible = "English Web Bible")) %>% 
  mutate(word = str_extract(word, "[a-z']+")) %>%
  count(bible, word) %>%
  group_by(bible) %>%
  mutate(proportion = n / sum(n)) %>% 
  select(-n) %>% 
  pivot_wider(names_from = bible, values_from = proportion) %>%
  pivot_longer(`American Standard Version`:`English Web Bible`,
               names_to = "bible", values_to = "proportion")
```

### Plot the frequency of words against The King James Version

```{r, out.width="50%" }
library(scales)
ggplot(frequency, aes(x = proportion, y = `King James Version`, 
                      color = abs(`King James Version` - proportion))) +
  geom_abline(color = "gray40", lty = 2) +
  geom_jitter(alpha = 0.1, size = 2.5, width = 0.3, height = 0.3) +
  geom_text(aes(label = word), check_overlap = TRUE, vjust = 1.5) +
  scale_x_log10(labels = percent_format()) +
  scale_y_log10(labels = percent_format()) +
  scale_color_gradient(limits = c(0, 0.001), 
                       low = "darkslategray4", high = "gray75") +
  facet_wrap(~bible, ncol = 2) +
  theme(legend.position="none") +
  labs(y = "King James Version", x = NULL)
```

# Sources
[Text Mining](https://www.tidytextmining.com/tidytext.html)

